Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-06-06 latex/afm-cs-main.tex
Update figures to latest.

\begin{figure*}
  \includesvg[width=1\textwidth]{figures/cs_raster_images_4-26-2019}
  \caption{Raster and compressed sensing images of a 5 micron square area of the
    CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
    indicated by the red line are shown in Fig.~\ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}

@@

\begin{figure*}[t!]
  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_4-26-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are included.}
  \label{fig:pixel_rows}
\end{figure*}

@@

\begin{figure*}
  \includesvg[width=1\linewidth]{figures/cs_raster_images_6-4-2019.svg}
  \caption{}
  \label{fig:many}
\end{figure*}

>>>>

% \begin{figure*}
%   \includesvg[width=1\textwidth]{figures/cs_raster_images_4-26-2019}
%   \caption{Raster and compressed sensing images of a 5 micron square area of the
%     CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
%     indicated by the red line are shown in Fig.~\ref{fig:pixel_rows}.}
%   \label{fig:resultsF1_images}
% \end{figure*}

\begin{figure*}
  \includesvg[width=1\linewidth]{figures/cs_raster_images_6-5-2019.svg}
  \caption{Raster and compressed sensing images of a 5 micron square area of the
     CS-20NG grating. All images are 512$\times$512 pixels: the raster images marked as 64 and 128 lines have been interpolated. The rows of pixels
     indicated by the red line are shown in Fig.~\ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}

@@

\begin{figure*}[t!]
  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_6-5-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are included.}
  \label{fig:pixel_rows}
\end{figure*}

@@
